\textsf{Are large language models superhuman chemists?}

### 2024-10-18 src/tex/appendix.tex

% \begin{figure}
%     \centering
%     \includegraphics[]{figures/cb_humanset_v1.pdf}
%     \caption{\textbf{Composition of the human subset.} The circular plot shows the distribution of topics and required skills in the human subset of the \chembench corpus. The human subset is a representative subset of the full corpus, with a balanced distribution of topics and skills.}
% \end{figure}

@@

\begin{table}
    \caption{\textbf{Performance of the models on the \chembench corpus.} The table shows the fraction of questions answered completely correctly by the models for different skills and difficulty levels.}
    \variable{output/performance_table.tex}
\end{table}

\begin{table}
    \caption{\textbf{Performance of the models on the \enquote{tiny} subset of the \chembench corpus.} The table shows the fraction of questions answered completely correctly by the models for different skills and difficulty levels.}
    \variable{output/performance_table_human_subset.tex}
\end{table}

\begin{figure}[htb]
    \centering
    \includegraphics{figures/all_questions_models_completely_correct_radar_overall.pdf}
    \caption{\textbf{Performance of the models on the different topics of the \chembench corpus.} The radar plot shows the performance of the models on the different topics of the \chembench corpus. The performance is measured as the fraction of questions answered completely correctly by the models.
    A score of 1 indicates that all questions were answered completely correctly, while a score of 0 indicates that none were answered completely correctly.
    }
    \label{fig:all_questions_models_completely_correct_radar_overall}
    \script{analyze_model_reports.py}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/cb_humanset_v2.pdf}
    \caption{\textbf{Composition of the human subset.} The circular plot shows the distribution of topics and required skills in the human subset of the \chembench corpus. The human subset is a representative subset of the full corpus, with a balanced distribution of topics and skills.}
\end{figure}

@@

\begin{table}
    \caption{\textbf{Performance of the models on the \chembench corpus.} The table shows the fraction of questions answered completely correctly by the models for different skills and difficulty levels.}
    \resizebox{\textwidth}{!}{
    \variable{output/performance_table.tex}
    }
\end{table}

\begin{table}
    \caption{\textbf{Performance of the models on the \enquote{tiny} subset of the \chembench corpus.} The table shows the fraction of questions answered completely correctly by the models for different skills and difficulty levels.}
    \resizebox{\textwidth}{!}{
    \variable{output/performance_table_human_subset.tex}
    }
\end{table}

\begin{figure}[htb]
    \centering
    \includegraphics[width=\textwidth]{figures/all_questions_models_completely_correct_radar_overall.pdf}
    \caption{\textbf{Performance of the models on the different topics of the \chembench corpus.} The radar plot shows the performance of the models on the different topics of the \chembench corpus. The performance is measured as the fraction of questions answered completely correctly by the models.
    A score of 1 indicates that all questions were answered completely correctly, while a score of 0 indicates that none were answered completely correctly.
    }
    \label{fig:all_questions_models_completely_correct_radar_overall}
    \script{analyze_model_reports.py}
\end{figure}
